% Please do not change the document class
\documentclass{tufte-handout}

% Please do not change these packages


% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{Mad Mechs Handout} 



\author{1507516}

\begin{document}

\maketitle


\section{Overview \& High concept}
Mad Mechs is a turn based strategy game featuring giant Mechs.
The game will feature a number of different systems, such as a in-depth customization system, detectable buildings and different factions.
The customization system will allow players to create a mech from a wide variety of parts. Each section can be equipped with a light, medium or heavy part. There will also be a large selection of different types of weapons that the mech can use.
The games aesthetic is a cell shaded borderlands style game, with cartoon style particle effects. 


\section{Technical Feasibility}
Currently most of the core components of the game are almost all there. There is a basic test level that contains building destruction, mech customization, cell shading, basic AI and Action Point based combat on a grid. 


\section{USP}
A title that is a large source of inspiration for this  game is XCOM series. The games are very popular on steam and have had over 1.8M sales according to steamspy.
Another similar style game is Invisible, Inc.

The target audience for this game are people who enjoy turn based strategy games, aged 18-40.

The unique selling point for this game is it’s detailed mech customization and the scale of the game. Furthermore the game has a unique building destruction system that will allow players to create a domino effect with buildings.




\end{document}


